---
title: "Get started with cbwsdid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using cbwsdid with the Simulated Panel Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

This vignette gives a compact tour of the main `cbwsdid` workflow using the
simulated dataset shipped with the package. The full dataset contains 500 units
observed from 2000 to 2012. To keep the vignette light enough, the examples below use a smaller subset.

```{r setup, message = FALSE}
library(cbwsdid)

data(cbwsdid_sim)

dat <- subset(cbwsdid_sim, id <= 150)

head(dat)
```

The simulated data have staggered absorbing treatment timing. The treatment year
is related to observed covariates, and untreated trends also depend on those
covariates. This makes the dataset useful for comparing unrefined weighted
stacked DID with covariate-balanced refinements.

## Weighted Stacked DID

Setting `refinement.method = "none"` estimates weighted stacked DID without a
first-stage matching or weighting refinement. The model returned by `cbwsdid()`
is a `fixest` object with additional metadata.

```{r weighted-stacked}
fit_ws <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 2),
  refinement.method = "none"
)

fit_ws
```


```{r weighted-metadata}

names(attr(fit_ws, "cbwsdid"))
```

The same fitted object can be summarized into dynamic, simple, pooled, and
cohort-level quantities of interest.

```{r weighted-qoi-d}
cbwsdid_qoi(fit_ws, type = "dynamic")
```


```{r weighted-qoi-s}
cbwsdid_qoi(fit_ws, type = "simple")
```


```{r weighted-qoi-p}
cbwsdid_qoi(fit_ws, type = "pooled")
```


```{r weighted-qoi-c}
cohort_ws <- cbwsdid_qoi(fit_ws, type = "cohort")
head(cohort_ws$dynamic)
cohort_ws$simple
```

Subexperiment diagnostics show which cohorts are used and how many treated and
control units enter the design.

```{r subexperiments}
subexp_ws <- cbwsdid_subexperiments(fit_ws)
```


```{r subexperiments-o}
subexp_ws$overall
```


```{r subexperiments-b}
subexp_ws$by_subexp
```

If you want the conventional unweighted stacked DID regression on the same
stacked sample, you can remove the final stacked weights from the returned
`fixest` model.

```{r unweighted-stacked}
fit_unweighted <- update(fit_ws, weights = NULL)

fit_unweighted
```


Since the `cbwsdid()` returns a `fixest` object, one can use such convinient functions as `fixest::iplot` or `fixest::etable`

```{r fixest-ex}
library(fixest)

iplot(fit_unweighted)
```



## Covariate-Balanced Refinement with WeightIt

The `weightit` backend estimates first-stage ATT weights inside each
subexperiment before the final stacked aggregation weights are applied.
Covariates can be written in a R formula syntax. A bare covariate is
read at event time `-1`.

```{r weightit-fit, message = FALSE, warning = FALSE}
fit_weightit <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 1),
  refinement.method = "weightit",
  covs.formula = ~ lag(outcome, 1:2) + lag(x1, 1:2),
  refinement.args = list(method = "glm")
)

cbwsdid_qoi(fit_weightit, type = "dynamic")
cbwsdid_qoi(fit_weightit, type = "simple")
```

Balance diagnostics are computed within subexperiments using the first-stage
refinement weights.

```{r weightit-balance}
bal_weightit <- cbwsdid_balance(fit_weightit)
bal_weightit$overall
```

## Covariate-Balanced Refinement with MatchIt

The `matchit` backend works similarly, but obtains the first-stage refinement
weights from matching. The `exact.formula` argument can be used for exact
matching or exact stratification variables.

```{r matchit-fit, message = FALSE, warning = FALSE}
fit_matchit <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 1),
  refinement.method = "matchit",
  covs.formula = ~ lag(outcome, 1:2) + lag(x1, 1:2),
  exact.formula = ~ x2,
  refinement.args = list(
    method = "nearest",
    distance = "mahalanobis",
    ratio = 3,
    replace = TRUE
  )
)

cbwsdid_qoi(fit_matchit, type = "simple")
cbwsdid_balance(fit_matchit)$overall
```

## Moderated Treatment Effects

The `moderation.formula` argument fits additional second-stage models in which
the treatment effect is interacted with pre-treatment moderators. The baseline
model remains available, while moderated models are stored in the metadata.

```{r moderation, message = FALSE, warning = FALSE}
fit_moderated <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 1),
  refinement.method = "weightit",
  covs.formula = ~ lag(outcome, 1:2) + lag(x1, 1:2),
  refinement.args = list(method = "glm"),
  moderation.formula = ~ lag(outcome, 1)
)


model <- attr(fit_moderated, "cbwsdid")

etable(model$pooled_moderation_model)

```

By default, moderated quantities are averaged over the observed moderator
distribution. You can also request effects at named moderator profiles. The
lagged moderator created by `lag(outcome, 1)` is named `outcome_l1`.

```{r moderation-newdata}
profiles <- data.frame(
  outcome_l1 = c(-1, 1)
)

cbwsdid_qoi(
  fit_moderated,
  type = "pooled",
  model_type = "moderated",
  newdata = profiles
)
```

## Switch-On Syntax

The package also supports repeated switch designs through `design = "switch01"`
and `design = "switch10"`. The simulated dataset is absorbing, so each treated
unit has at most one admissible `0 -> 1` switch and there are no switch-off
episodes. The switch-on syntax can still be demonstrated on the same data.

```{r switch01}
fit_switch01 <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 1),
  design = "switch01",
  history.length = 2,
  first_switch_only = TRUE,
  refinement.method = "none"
)

cbwsdid_subexperiments(fit_switch01)$overall
cbwsdid_qoi(fit_switch01, type = "simple")
```

For recurrent switch-off designs, use `design = "switch10"` with data that
contain admissible `1 -> 0` episodes:

```{r switch10-syntax, eval = FALSE}
fit_switch10 <- cbwsdid(
  data = recurrent_panel,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 1),
  design = "switch10",
  history.length = 2,
  refinement.method = "weightit",
  covs.formula = ~ lag(outcome, 1:2) + lag(x1, 1:2)
)
```

## Memory and Parallel Options

By default, `cbwsdid()` keeps the stacked estimation sample in the model
metadata. This is needed for `type = "cohort"`. If memory is a concern and
cohort-level post-estimation will not be used, set `keep_data = FALSE`.

```{r keep-data}
fit_light <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 1),
  refinement.method = "none",
  keep_data = FALSE
)

is.null(attr(fit_light, "cbwsdid")$stacked.data)
```

Large sets of subexperiments can be refined in parallel when the optional
`future` and `future.apply` packages are installed:

```{r parallel-syntax, eval = FALSE}
fit_parallel <- cbwsdid(
  data = cbwsdid_sim,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 1),
  refinement.method = "weightit",
  covs.formula = ~ lag(outcome, 1:2) + lag(x1, 1:2),
  refinement.args = list(method = "glm"),
  parallel = TRUE,
  slaves = 2
)
```
