---
title: "Get started with cbwsdid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with cbwsdid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

`cbwsdid` implements Covariate-Balanced Weighted Stacked Difference-in-Differences
(CBWSDID). The estimator follows the weighted stacked DID logic of Wing,
Freedman, and Hollingsworth (2024) for across-subexperiment aggregation, but
adds a first-stage design refinement inside each subexperiment. In practice, this means that matching or weighting is
used to improve treated-control comparability within each cohort-specific
subexperiment, while the final stacked weights continue to target the trimmed
aggregate ATT.

This short vignette uses the simulated panel dataset shipped with the package.
Treatment timing in this dataset is related to observed covariates, and
untreated outcome trends also depend on those covariates. That makes it useful
for seeing why the refinement step is part of the main workflow.

```{r setup, message = FALSE}
library(cbwsdid)
library(ggplot2)

data(cbwsdid_sim)

dat <- subset(cbwsdid_sim, id <= 150)
head(dat)
```

## Estimate CBWSDID

The main call below uses `refinement.method = "weightit"`. The covariates in
`covs.formula` are read at pre-treatment event times inside each subexperiment;
for example, `lag(outcome, 1:2)` uses the outcome measured one and two periods
before treatment in the corresponding subexperiment.

```{r fit-weightit, message = FALSE, warning = FALSE}
fit_cbws <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 2),
  refinement.method = "weightit",
  covs.formula = ~ lag(outcome, 1:2) + lag(x1, 1:2),
  refinement.args = list(method = "glm")
)

fit_cbws
```

`cbwsdid()` returns a `fixest` model object. The package-specific metadata is
stored in `attr(fit, "cbwsdid")`.

```{r metadata}
names(attr(fit_cbws, "cbwsdid"))
```

## Quantities of interest

The event-study coefficients can be reported directly, but `cbwsdid_qoi()`
also returns compact post-estimation summaries.

```{r qoi}
dynamic_cbws <- cbwsdid_qoi(fit_cbws, type = "dynamic")
simple_cbws <- cbwsdid_qoi(fit_cbws, type = "simple")

dynamic_cbws
simple_cbws
```

The reported standard errors are conditional cluster-robust intervals
(clustered by unit, with the design weights treated as fixed). Analytic
influence-function and pipeline-bootstrap alternatives are available through
the `se.method` argument of `cbwsdid_qoi()`.

The dynamic table is ready to plot.

```{r dynamic-plot}
ggplot(dynamic_cbws, aes(x = et, y = estimate)) +
  geom_hline(yintercept = 0, color = "grey55", linewidth = 0.3) +
  geom_vline(xintercept = -0.5, color = "grey75", linetype = "dashed") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.08) +
  geom_point(size = 2) +
  geom_line(linewidth = 0.4) +
  scale_x_continuous(breaks = sort(dynamic_cbws$et)) +
  labs(x = "Event time", y = "ATT")
```

Balance and subexperiment diagnostics are also available from the same fitted
object. In the balance table, `smd.un` holds standardized mean differences on
the full design sample and `smd.adj` after applying the refinement weights, so
the comparison shows how much the first stage improved comparability; adjusted
values within roughly 0.1 of zero are a common benchmark. The subexperiment
summary reports which cohorts entered estimation and the size of their raw and
refined donor pools.

```{r diagnostics}
cbwsdid_balance(fit_cbws)$overall
cbwsdid_subexperiments(fit_cbws)$overall
```

## Compare with unrefined weighted stacked DID

To fit weighted stacked DID without the first-stage refinement, set
`refinement.method = "none"`. The comparison changes the within-subexperiment
design adjustment while leaving the stacked DID event-study specification
otherwise aligned.

```{r fit-none}
fit_ws <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 2),
  refinement.method = "none"
)

cbwsdid_qoi(fit_ws, type = "dynamic")
```

Because both fitted objects are `fixest` models, `fixest::iplot()` can put the
two event studies on the same figure.

```{r compare-iplot}
fixest::iplot(
  list(
    "CBWSDID (WeightIt)" = fit_cbws,
    "Weighted stacked DID" = fit_ws
  ),
  ref.line = -1,
  main = "Dynamic effects with and without refinement"
)
```

## Where to go next

The `quantities-of-interest` vignette covers the full set of post-estimation
summaries (pooled and cohort effects, moderated effects, bootstrap inference);
the `sensitivity-analysis` vignette shows how to feed CBWSDID event-study
estimates into `HonestDiD`.
