---
title: "Quantities of interest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quantities of interest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

This vignette shows how to extract and present quantities of interest from a
fitted `cbwsdid` model. The same fitted object can be used for dynamic effects,
simple post-treatment averages, pooled ATT estimates, cohort-level summaries,
and moderated treatment effects.

```{r setup, message = FALSE}
library(cbwsdid)
library(ggplot2)

data(cbwsdid_sim)
dat <- subset(cbwsdid_sim, id <= 150)
```

The example below uses covariate-balanced weighting and asks for two
pre-treatment moderators: the binary baseline covariate `x2` and the
pre-treatment lagged outcome `lag(outcome, 1)`. The latter is stored under the
generated name `outcome_l1`.

```{r fit-qoi, message = FALSE, warning = FALSE}
fit_qoi <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-2, 2),
  refinement.method = "weightit",
  covs.formula = ~ lag(outcome, 1:2) + lag(x1, 1:2),
  refinement.args = list(method = "glm"),
  moderation.formula = ~ x2 + lag(outcome, 1)
)

```

## Overall QOI

`type = "dynamic"` returns event-time effects relative to the omitted reference
period `et = -1`.

```{r qoi-dynamic}
cbwsdid_qoi(fit_qoi, type = "dynamic")
```

`type = "simple"` averages the selected post-treatment event-time effects. By
default, all available post-treatment periods are used.

```{r qoi-simple}
cbwsdid_qoi(fit_qoi, type = "simple")
cbwsdid_qoi(fit_qoi, type = "simple", post = 0:1)
```

`type = "pooled"` is the equally weighted average of post-treatment dynamic
effects minus the equally weighted average of pre-treatment placebo effects
at event times `-2` and earlier. It is therefore a placebo-corrected overall
effect, while `type = "simple"` is only the post-treatment average. The overall
pooled QOI is derived from the dynamic model and works even when the model was
fitted with `pooled = FALSE`.

```{r qoi-pooled}
cbwsdid_qoi(fit_qoi, type = "pooled")
```

`type = "cohort"` returns a list with cohort-level dynamic effects and simple
post-treatment averages. This uses the stacked estimation data stored by
`keep_data = TRUE`, which is the default.

```{r qoi-cohort}
cohort_qoi <- cbwsdid_qoi(fit_qoi, type = "cohort")

head(cohort_qoi$dynamic)
cohort_qoi$simple
```

Finally, pipeline-bootstrap inference is available for the same quantities.
Each draw resamples units (the clusters) and re-runs the entire pipeline —
subexperiment construction, refinement, stacked weighting, and QOI
aggregation — so the intervals reflect the uncertainty of the first stage as
well. The same machinery powers `cbwsdid_qoi(..., se.method = "bootstrap")`,
which returns the usual QOI table with bootstrap standard errors, while
`se.method = "analytic"` provides influence-function standard errors for
overall quantities.

```{r qoi-bootstrap}
boot_qoi <- cbwsdid_bootstrap(fit_qoi,
                              data = dat,
                              B = 10, # kept tiny for the example; use B = 999+ in real analyses
                              qoi = "dynamic")
boot_qoi
```


## Moderated QOI

When `moderation.formula` is supplied, `cbwsdid()` estimates additional
second-stage models in which the treatment effect is interacted with the
specified pre-treatment moderators. These models also include
moderator-by-event-time main effects, so weighted controls can estimate
moderator-dependent counterfactual trends. The treatment-by-moderator
coefficients are therefore DID-in-slopes parameters rather than raw treated
gradients. The main returned model remains the overall event-study model;
moderated models are stored in the metadata.

```{r moderated-average}
cbwsdid_qoi(fit_qoi, type = "dynamic", model_type = "moderated")
cbwsdid_qoi(fit_qoi, type = "simple", model_type = "moderated")
```

The default moderated QOI is evaluated at the treated unit-by-stack mean
moderator profile from the original fit. The raw `treated_sa` coefficients in
the moderated regression are effects at moderator value zero, so profile-based
QOIs are usually the safer way to report marginal effects.
For moderation hypotheses, it is often more useful to evaluate the effect over a
grid of substantively meaningful moderator values and draw a marginal plot.

```{r marginal-profiles}
moderator_reference <- attr(fit_qoi, "cbwsdid")$moderation.reference

outcome_grid <- seq(
  stats::quantile(moderator_reference$outcome_l1, 0.10, na.rm = TRUE),
  stats::quantile(moderator_reference$outcome_l1, 0.90, na.rm = TRUE),
  length.out = 25
)

marginal_profiles <- expand.grid(
  outcome_l1 = outcome_grid,
  x2 = c(0, 1)
)

simple_margins <- cbwsdid_qoi(
  fit_qoi,
  type = "simple",
  model_type = "moderated",
  newdata = marginal_profiles
)

simple_margins$x2_label <- factor(
  simple_margins$x2,
  levels = c(0, 1),
  labels = c("x2 = 0", "x2 = 1")
)

head(simple_margins)
```

```{r marginal-plot}
ggplot(
  simple_margins,
  aes(x = outcome_l1, y = estimate, color = x2_label, fill = x2_label)
) +
  geom_hline(yintercept = 0, linewidth = 0.3) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25,
              color = NA) +
  geom_line(linewidth = 0.6) +
  labs(
    x = "Lagged outcome at event time -1",
    y = "Simple post-treatment ATT",
    color = NULL,
    fill = NULL
  )+
  theme_bw()
```

The same idea works for dynamic profiles. Here the effect is evaluated at low
and high values of the lagged outcome for each value of `x2`.

```{r dynamic-profiles}
profile_values <- expand.grid(
  outcome_l1 = stats::quantile(
    moderator_reference$outcome_l1,
    c(0.25, 0.75),
    na.rm = TRUE
  ),
  x2 = c(0, 1)
)

dynamic_profiles <- cbwsdid_qoi(
  fit_qoi,
  type = "dynamic",
  model_type = "moderated",
  newdata = profile_values
)

dynamic_profiles$profile_label <- paste0(
  "x2 = ", dynamic_profiles$x2,
  ", outcome_l1 = ", round(dynamic_profiles$outcome_l1, 2)
)

ggplot(dynamic_profiles, aes(x = et, y = estimate, color = profile_label)) +
  geom_hline(yintercept = 0, color = "grey55", linewidth = 0.3) +
  geom_vline(xintercept = -0.5, color = "grey75", linetype = "dashed") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.08,
                alpha = 0.75) +
  geom_point(size = 1.8) +
  geom_line(linewidth = 0.4) +
  scale_x_continuous(breaks = sort(unique(dynamic_profiles$et))) +
  labs(x = "Event time", y = "ATT", color = NULL)
```

The event-time path of moderation slopes is available directly. Pre-treatment
slopes are placebo checks for moderator-dependent untreated trends.

```{r moderation-slopes}
cbwsdid_qoi_moderation_slopes(fit_qoi)
```

Pipeline bootstrap inference is also available for moderated QOIs. Moderator
profiles are resolved once from the original fit and then held fixed across
bootstrap draws.

```{r moderated-bootstrap}
cbwsdid_qoi(
  fit_qoi,
  type = "dynamic",
  model_type = "moderated",
  se.method = "bootstrap",
  B = 10, # tiny for the example
  seed = 123
)
```

## Regression tables

Since `cbwsdid()` returns `fixest` objects and stores additional `fixest` models
in the metadata, the usual `fixest::etable()` workflow can be used for
regression-style tables.

```{r etable-dynamic}
meta <- attr(fit_qoi, "cbwsdid")

fixest::etable(
  fit_qoi,
  meta$moderation_model,
  keep = "treated"
)
```

The standalone pooled overall and pooled moderated regressions stored for
backward compatibility can be tabulated in the same way. Their coefficients
need not equal the equal-weighted overall pooled QOI on unbalanced panels.

```{r etable-pooled}
fixest::etable(
  meta$pooled_model,
  meta$pooled_moderation_model,
  keep = "treated"
)
```
