---
title: "Sensitivity analysis with HonestDiD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sensitivity analysis with HonestDiD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

This vignette shows the basic bridge between a `cbwsdid` event-study model and
the `HonestDiD` sensitivity-analysis workflow. The key step is to pass the
estimated event-study coefficients and their covariance matrix to HonestDiD in
the correct event-time order.

```{r setup, message = FALSE}
library(cbwsdid)

honestdid_available <- requireNamespace("HonestDiD", quietly = TRUE)

data(cbwsdid_sim)
dat <- subset(cbwsdid_sim, id <= 150)
```

We start from the same kind of CBWSDID model as in the getting-started vignette,
but use a slightly wider event window so that there are two estimated
pre-treatment coefficients before the reference period `et = -1`.

```{r fit-sensitivity, message = FALSE, warning = FALSE}
fit_sens <- cbwsdid(
  data = dat,
  y = "outcome",
  d = "D",
  id = c("id", "year"),
  kappa = c(-3, 3),
  refinement.method = "weightit",
  covs.formula = ~ lag(outcome, 1:3) + lag(x1, 1:3),
  refinement.args = list(method = "glm")
)

cbwsdid_qoi(fit_sens, type = "dynamic")
```

## Extract event-study inputs

HonestDiD expects a coefficient vector and covariance matrix ordered as
pre-treatment coefficients followed by post-treatment coefficients. The
reference period is omitted from the model, so it is not included in these
objects.

```{r honestdid-inputs}
event_study_terms <- grep(
  "^et::(-?[0-9]+):treated_sa$",
  names(stats::coef(fit_sens)),
  value = TRUE
)

event_time <- as.integer(
  sub("^et::(-?[0-9]+):treated_sa$", "\\1", event_study_terms)
)

event_order <- order(event_time)
event_study_terms <- event_study_terms[event_order]
event_time <- event_time[event_order]

betahat <- stats::coef(fit_sens)[event_study_terms]
sigma <- stats::vcov(fit_sens)[event_study_terms, event_study_terms]

num_pre_periods <- sum(event_time < 0)
num_post_periods <- sum(event_time >= 0)

data.frame(
  event_time = event_time,
  estimate = unname(betahat)
)
```

The vector `l_vec` selects the post-treatment scalar parameter. The example
below uses the average of all post-treatment event-time effects.

```{r l-vec}
l_vec <- rep(1 / num_post_periods, num_post_periods)
l_vec
```

## Run HonestDiD

If `HonestDiD` is installed, the following chunks compute the usual confidence
set and then robust confidence sets for a small grid of smoothness-deviation
values `M`.

```{r honestdid-results, eval = honestdid_available}
original_cs <- HonestDiD::constructOriginalCS(
  betahat = betahat,
  sigma = sigma,
  numPrePeriods = num_pre_periods,
  numPostPeriods = num_post_periods,
  l_vec = l_vec,
  alpha = 0.05
)

robust_cs <- HonestDiD::createSensitivityResults(
  betahat = betahat,
  sigma = sigma,
  numPrePeriods = num_pre_periods,
  numPostPeriods = num_post_periods,
  l_vec = l_vec,
  Mvec = seq(0, 0.5, by = 0.25),
  alpha = 0.05
)

original_cs
robust_cs
```

```{r honestdid-plot, eval = honestdid_available}
HonestDiD::createSensitivityPlot(
  robustResults = robust_cs,
  originalResults = original_cs,
  maxM = max(robust_cs$M)
)
```

The same extraction pattern can be reused with different `l_vec` choices. For
example, `c(1, 0, 0, 0)` selects the first post-treatment effect when the model
has four post-treatment event times, while `rep(1 / 4, 4)` averages them.
